Generating Performance Improvement Suggestions by using Cross-Organizational Process Mining

### 2015-09-16 1_introduction/introduction.tex
no message

The approach proposed in this study is a four-stage solution and it starts with mining the process models of organizations; followed by performance indicator analysis and then mismatch pattern analysis. Finally in the suggestion generation stage, learning opportunities are created for each organization. With this approach it is aimed to help business process management users to focus on the potentially important parts of their business maps. Proposed methodology is implemented in ProM framework \cite{verbeek2010prom} as a set of plugins corresponding for each stage and packaged under the name of \textit{CrossOrgProcMin} and tested on a synthetic and real-life event logs. Performance of methodology is assessed with a set of defined evaluation metrics for each stage and resulting recommendations are presented to show how this approach helps users to focus on learning opportunities between organizations with a performance improvement potential.

>>>>

The approach proposed in this study is a four-stage solution and it starts with mining the process models of organizations; followed by performance indicator analysis and then mismatch pattern analysis. Finally in the suggestion generation stage, learning opportunities are created for each organization. With this approach it is aimed to help business process management users to focus on the potentially important parts of their business maps. Proposed methodology is implemented in ProM framework \cite{verbeek2010prom} as a set of plug-ins corresponding for each stage and packaged under the name of \textit{CrossOrgProcMin} and tested on a synthetic and real-life event logs. Performance of methodology is assessed with a set of defined evaluation metrics for each stage and resulting recommendations are presented to show how this approach helps users to focus on learning opportunities between organizations with a performance improvement potential.

### 2015-09-16 5_results_discussions/coselog-wabo/coselog-wabo.tex
no message

\subsection{Environmental Permit Application Process}
\label{subsec:coselog-wabo-process}
\textit{Environmental Permit Application Process} dataset originates from the "Configurable Services for Local Governments (CoSeLoG)" project \cite{van2011business} which investigates the similarities and dissimilarities between several processes of different municipalities in Netherlands. Dataset contains records of receiving phase for the building permit application process in 5 municipalities, which are comparable since activity labels in the different event logs refer to the same activities performed in five municipalities. In this dataset \cite{coselog-data}, there are total of 1214 cases and 2142 events with a variable distribution between event logs of municipalities and municipalities are used as organizational logs.

\begin{itemize}
  \item In \textit{Process Model Mining} stage, with 10\% of noise threshold, high fitness values are achieved; however, some of the process models like Municipality \#4 and \#5 resulted with low appropriateness values. 
  \item In \textit{Performance Indicator Analysis} stage, after calculating the performance indicators, municipalities are clustered and three clusters are created: Municipality \#1 is located in the first cluster; Municipality \#2 and \#4 are located in the second cluster; and Municipality \#3 and \#5 are grouped in to the last cluster.
  \item In \textit{Mismatch Pattern Analysis} stage, it can be stated that as the similarity between process models of municipalities increases, number of mismatch patterns decreases on most of the cases. When further analyzed, it can be seen that Municipalities \#4 and \#5, which have significantly more complex process model compared to others, fails in spotting mismatch patterns according to \textit{graph-edit similarity}.
  \item In \textit{Recommendation Generation} stage, for different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:coselog-wabo-recommendation-generation-analysis} for the thresholds of 25 \%, 50 \% and 75 \% since these are the breaking points. For instance, cluster of Municipality \#1 performs worse in 6 indicators with the difference of 25 \% and on average 5 mismatch patterns are listed for each performance indicator. When it is compared to the total mismatch patterns of Municipality #1, which is 357, proposed approach helps significantly to the user for focusing performance improvement.
	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{5_results_discussions/coselog-wabo/recommendation-generation-analysis-k3}
		\caption{Recommendation Generation analysis for Environmental Permit Application Process dataset (3 Clusters)}
	  \label{fig:coselog-wabo-recommendation-generation-analysis-k3}
	\end{figure}
\end{itemize}

>>>>

\subsection{Environmental Permit Application Process}
\label{subsec:coselog-wabo-process}
\textit{Environmental Permit Application Process} dataset originates from the "Configurable Services for Local Governments (CoSeLoG)" project \cite{van2011business} which investigates the similarities and dissimilarities between several processes of different municipalities in Netherlands. Dataset contains records of receiving phase for the building permit application process in 5 municipalities, which are comparable since activity labels in the different event logs refer to the same activities performed in five municipalities. In this dataset \cite{coselog-data}, there are 1214 cases and 2142 events with a variable distribution between event logs of municipalities and municipalities are used as organizational logs.

\begin{itemize}
  \item In \textit{Process Model Mining} stage, with 10 \% of noise threshold, high fitness values are achieved; however, some of the process models like Municipality \#4 and \#5 resulted with low appropriateness values. 
  \item In \textit{Performance Indicator Analysis} stage, after calculating the performance indicators, municipalities are clustered and three clusters are created: Municipality \#1 is located in the first cluster; Municipality \#2 and \#4 are located in the second cluster; and Municipality \#3 and \#5 are grouped in to the last cluster.
  \item In \textit{Mismatch Pattern Analysis} stage, it can be stated that as the similarity between process models of municipalities increases, number of mismatch patterns decreases for most of the cases. When further analyzed, it can be seen that Municipalities \#4 and \#5, which have significantly more complex process models compared to others, fail in spotting mismatch patterns under \textit{graph-edit similarity}.
  \item In \textit{Recommendation Generation} stage, for different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:coselog-wabo-recommendation-generation-analysis} for the thresholds of 25 \%, 50 \% and 75 \% since these are the breaking points. For instance, cluster of Municipality \#1 performs worse in 6 indicators with the difference of 25 \% and on average 5 mismatch patterns are listed for each performance indicator. When it is compared to the total mismatch patterns of Municipality \#1, which is 357, proposed approach helps significantly to the user for focusing performance improvement.
	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{5_results_discussions/coselog-wabo/recommendation-generation-analysis-k3}
		\caption{Recommendation Generation analysis for Environmental Permit Application Process dataset (3 Clusters)}
	  \label{fig:coselog-wabo-recommendation-generation-analysis}
	\end{figure}
\end{itemize}

### 2015-09-16 paper.tex
no message

\title{Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining}
%If Title is too long, use \titlerunning
\titlerunning{Cross-Organizational Process Mining}

@@

\begin{abstract}
Process mining is a relatively young and developing research area with the main idea of discovering, monitoring and improving processes by extracting information from the event logs. With the increase of cloud computing and shared infrastructures, event logs of multiple organizations are available for analysis where cross-organizational process mining stands with the opportunity for organizations learning from each other. The approach proposed in this study mines process models of organizations and calculates performance indicators; followed by clustering of organizations based on performance indicators and finally spots mismatches between the process models to generate recommendations. This approach is implemented as extensible and configurable plugin set in ProM framework and tested by synthetic and real life logs where successful and suitable results are achieved within evaluation metrics. Generated recommendation results indicate that the use of this approach can help users to focus on the areas of process models with potential performance improvement, which are difficult to spot manually and visually.
\end{abstract}

>>>>

\title{Generating Performance Improvement Suggestions by using Cross-Organizational Process Mining}
%If Title is too long, use \titlerunning
\titlerunning{Cross-Organizational Process Mining}

@@

\begin{abstract}
Process mining is a relatively young and developing research area with the main idea of discovering, monitoring and improving processes by extracting information from event logs. With the increase of cloud computing and shared infrastructures, event logs of multiple organizations are available for analysis where cross-organizational process mining stands with the opportunity for organizations learning from each other. The approach proposed in this study mines process models of organizations and calculates performance indicators; followed by clustering of organizations based on performance indicators and finally spots mismatches between the process models to generate recommendations. This approach is implemented as an extensible and configurable plug-in set in ProM framework and tested by synthetic and real life logs where successful and suitable results are achieved within evaluation metrics. Generated recommendation results indicate that the use of this approach can help users to focus on the parts of process models with potential performance improvement, which are difficult to spot manually and visually.
\end{abstract}
